Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-01-28 joss/paper.Rmd
Edits to make simple script the prov example

```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")
script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")
script <- script.long
```

@@

code_graph(script)

@@

```{R long-setup, echo = FALSE, eval = TRUE}

>>>>

```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
library(Rclean)
```

@@

script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")
code_graph(script)

@@

```{R long-setup, echo = FALSE, eval = TRUE, results = "hide"}

script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")
script <- script.long
```

```{R long-script, echo = FALSE, eval = TRUE}
